---
title       : Developing Data Products Presentation     
subtitle    : Coursera devdataprod-012  
author      : Tony Mazzola
job         : 
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : [bootstrap, quiz, shiny, interactive]   # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
---

## Introduction

The intent of this presentation is to introduce the reader to my Shiny app.
The data used in the app is the mtcars data.  As a sample I have the first five records below:

```{r echo=FALSE}
head(mtcars)
```

--- .class #id

## Application Processing

The Shiny application prompts the user to input a car cylinder number.  Car cylinders only come
in 4, 6 or 8.  Once the user selects a  car cylinder, the app will do the following:

        1. Return the number you entered
        2. Return the Minimun Displacement
        3. Return the Mean Displacement
        4. Return the Maximum Displacement

--- .class #id

On this page I will show some sample output of the application.


1. Number of cylinders selected:
```{r echo=FALSE}
library(UsingR)
data(mtcars)
No_cyl <- 6
No_cyl
```

2. Minimum Displacement:
```{r echo=FALSE}
library(UsingR)
data(mtcars)
No_cyl <- 6
newdatatemp <- subset(mtcars, cyl == No_cyl)
minDisp=min(newdatatemp$disp)
return(round(minDisp))

```

3. Maximum Displacement:
```{r echo=FALSE}
library(UsingR)
data(mtcars)
No_cyl <- 6
newdatatemp <- subset(mtcars, cyl == No_cyl)
maxDisp=max(newdatatemp$disp)
return(round(maxDisp))

```

4. Mean Displacement:
```{r echo=FALSE}
library(UsingR)
data(mtcars)
No_cyl <- 6
newdatatemp <- subset(mtcars, cyl == No_cyl)
meanDisp=mean(newdatatemp$disp)
return(round(meanDisp))

```


--- .class #id


## Summary

This very basic Shiny application demonstrates the folowing: 

1. The various widgets of the 'shiny' tool.
2. An understanding of the process of publishing an application in shiny
3. An interface with R using embedded R code


